\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage{geometry}
\geometry{a4paper, margin=0.6in, top=0.5in, bottom=0.5in}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{fontspec}
\usepackage{xcolor}

% Typography - Using Inter for that high-end tech aesthetic
\setmainfont{Inter}

% Color Definition
\definecolor{primary}{RGB}{30, 30, 30}

% Formatting
\setlist{noitemsep, topsep=1pt, leftmargin=1.2em}
\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{6pt}

% Indentation environment for structured details
\newenvironment{subs}
  {\begin{adjustwidth}{1.2em}{0pt}}
  {\end{adjustwidth}}

% Custom command for Job/Project headers - Optimized for ATS
\newcommand{\entryheader}[4]{
    \noindent\textbf{#1} \hfill #2 \\
    \textit{#3} \hfill \small #4
}

\begin{document}

\pagestyle{empty}
\color{primary}

% Header
\begin{center}
    \textbf{\huge DAVID ZAHEMEN YEBOAH}\\[6pt]
    \small AI Engineer \& Software Developer\\[4pt]
    \small Kumasi, Ghana | \href{mailto:davidzahemenyeboah@gmail.com}{davidzahemenyeboah@gmail.com} | \href{https://david-z-yeboah.vercel.app}{Portfolio} | \href{https://github.com/zahemen9900}{GitHub} | +233598020802
\end{center}

%------------------------
\section*{Professional Summary}
\begin{subs}
AI/ML Engineer focused on productionizing deep learning systems, from model training and evaluation to low-latency API deployment on AWS/GCP. Strong in LLM adaptation (\textbf{PEFT/QLoRA}), ONNX optimization, and full-stack delivery of end-to-end AI products.
\end{subs}

%------------------------
\section*{Core Competencies}
\begin{subs}
    \textbf{Modeling \& Architecture:} Transformers, Supervised Contrastive Learning (SupCon), RAG, Agentic Multi-step Reasoning, Time-Series Forecasting.\\
    \textbf{MLOps \& Infrastructure:} PyTorch, TensorFlow, Hugging Face (PEFT/LoRA), ONNX Runtime, SageMaker, Vertex AI, Docker, CI/CD, ETL Design.\\
    \textbf{Development \& Deployment:} FastAPI, Next.js, React, TypeScript, Flutter, Supabase, Firebase, Git.
\end{subs}

%------------------------
\section*{Employment History}

\begin{subs}
    \entryheader{ML Engineer}{February 2025 -- Present}{Asaphic Ltd.}{Remote}
    \begin{itemize}
        \item \textbf{Audio Signal Processing:} Trained and deployed deep learning transformer models for real-time audio source separation with distributed training techniques (DDP), achieving high-fidelity signal enhancement and outperforming SOTA source separation models like Demucs-v4 and Spleeter by 30\%.
        \item \textbf{Infrastructure:} Engineered automated MLOps pipelines on AWS (SageMaker, Lambda, S3) for scalable, low-latency inference cycles.
        \item \textbf{Optimization:} Implemented adaptive tuning, ONNX compression and model pruning to reduce cloud inference costs by \textbf{35\%} while maintaining model precision.
        \item \textbf{Deployment:} Co-implemented an intelligent FastAPI backend service handling and re-routing large-volume AI requests over several models via API Gateway.
    \end{itemize}

    \vspace{6pt}

    \entryheader{Data Science Intern}{November 2024 -- December 2024}{Boston Consulting Group (BCGX)}{Remote}
    \begin{itemize}
        \item \textbf{Distributed Training:} Developed multi-GPU training pipelines for 3B-parameter models, reducing wall-clock training time by \textbf{65\%} via Distributed Data Parallel (DDP).
        \item \textbf{Data Engineering:} Orchestrated high-throughput extraction pipelines, processing 250M+ tokens from complex financial reports using context-aware chunking.
        \item \textbf{Memory Management:} Applied 4/8-bit quantization and PEFT/LoRA, reducing peak VRAM utilization by \textbf{70\%} during domain-specific fine-tuning.
    \end{itemize}
\end{subs}

%------------------------
\section*{Project Portfolio}

\begin{subs}
    \textbf{SignifyAI | Real‑Time Sign Language API Platform} \hfill \small\href{https://www.signify-ai.org}{signify-ai.org} \textbar{} \href{https://github.com/zahemen9900/gsl-tests}{GitHub}
    \begin{itemize}
        \item Led end-to-end development of a bidirectional Ghanaian Sign Language stack: \textbf{Sign2Text} (MediaPipe pose sequences to text) and \textbf{Text2Sign} (text-conditioned GAN-NAT generation of 540-dim pose motion).
        \item Built VM-based model pipelines on GCP covering canonicalized landmark preprocessing, motion/visibility quality gating, global-stat normalization, text-variation augmentation, and deployment-aligned training/evaluation (closed-set, unseen holdout, open-set abstention).
        \item Deployed and operated a \textbf{FastAPI} backend on Google Cloud Run with versioned GCS artifact loading, startup/readiness orchestration for both model services, and observability for inference quality and reliability.
        \item Added production-facing inference interfaces for static and near real-time use: Sign2Text low-latency APIs plus Text2Sign chunked/streamed generation endpoints with deterministic seeded outputs.
    \end{itemize}

    \vspace{4pt}

    \textbf{Agora | On-Chain Multi-Agent Arbitration Platform} \hfill \small\href{https://agora-bay-seven.vercel.app}{Web App} \textbar{} \href{https://pypi.org/project/agora-arbitrator-sdk/}{PyPI SDK} \textbar{} \href{https://github.com/zahemen9900/agora}{GitHub}
    \begin{itemize}
        \item Shipped a full-stack polyglot platform end-to-end: \textbf{FastAPI} backend on Google Cloud Run, \textbf{React 19} + TypeScript web app on Vercel, Anchor/\textbf{Solana} smart contracts, and published \texttt{agora-arbitrator-sdk} to \textbf{PyPI} (17 alpha releases; 3 execution modes: hosted API, local callable, BYOK multi-provider).
        \item Engineered three \textbf{LangGraph}-compiled deliberation engines --- Debate (devil's advocate cross-examination \& claim locking), ISP-weighted Confidence Vote, and Delphi --- routed by a \textbf{Thompson Sampling contextual bandit} that selects the optimal mechanism per task category for a 4-agent ensemble spanning Gemini, Claude, and OpenRouter.
        \item Designed real-time convergence monitoring with \textbf{Shannon entropy} and \textbf{Jensen-Shannon divergence}, enabling adaptive early termination and mid-run mechanism switching; implemented buffered SSE event streaming with replay for live deliberation visualization.
        \item Generated deterministic \textbf{Merkle transcript receipts} (SHA-256 hashed agent outputs committed to Solana devnet) with OpenTelemetry tracing for per-model token-level cost accounting, providing tamper-evident auditability of AI deliberation outcomes.
    \end{itemize}
\end{subs}

%------------------------
\section*{Awards}
\begin{subs}
\textbf{NASA Space Apps Challenge 2025 -- Galactic Impact Award Winner (\href{https://bioquery.vercel.app}{BioQuery})}
\end{subs}

%------------------------
\section*{Education \& Leadership}
\begin{subs}
    \entryheader{BSc. Computer Science}{September 2025}{Kwame Nkrumah Univ. of Science and Technology}{Ghana}
    \begin{itemize}
        \item \textbf{Academic Standing:} First Class Honors with 75.0\% CWA (approx. 3.7/4 GPA equivalent).
        \item \textbf{Leadership:} Committee Lead for AI research, KNUST AI \& Data Science Club; active contributor to GDSC and KNUST Robotics Club.
    \end{itemize}
\end{subs}

\end{document}
